Stochastic Newton with Arbitrary Sampling

### 2023-03-01 paper/main.tex
small fixes

	We discuss the problem of empirical risk minimization (ERM). The objective function $f$ (\ref{ERM}) is the average of a big number of functions $f_i$. In fact each $f_i$ is the loss on the $i$-th train data point. For example, this notation can be attributed to linear regression. In this case we try to fit the model's parameter vector $x$ to minimize the mean squared error (MSE) on the train data. \\

@@

	In our work we will assume the functions $f_i$ to satisfy the same regularity conditions that were originally introduced in \cite{kovalev2019stochastic}.

@@

	We will be applying different sampling strategies for the Algorithm 1 from \cite{kovalev2019stochastic}:

@@

	We aim to explore different sampling strategies for the Algorithm \ref{SN} in order to obtain practical improvements and their theoretical explainations.

>>>>

	We consider classical empirical risk minimization (ERM) which typically arises in many machine learning problems to train a model. The objective function $f$ (\ref{ERM}) is an average of a big number of functions $f_i$, where $f_i$ represents a loss on the $i$-th train data point. For example, this notation can be attributed to linear regression. In this case the goal is to find optimal model parameters $x$ that minimize the mean squared error (MSE) on the train data. \\

@@

	We make standard assumptions on functions $f_i$; the same that were originally takei into account in \cite{kovalev2019stochastic}.

@@

	We apply different sampling strategies on top of the Algorithm 1 from \cite{kovalev2019stochastic}:

@@

	We aim to explore different sampling strategies for the Algorithm \ref{SN} proving convergence guarantees and showing practical improvements over the baseline strategy.
